On the probability of finding a nonphysical solution through shadowing

### 2020-10-14 main.tex
fix typos upto defining tilted conjugacy map

For every solution $\hat{x}_i,i=0,\ldots$ satisfying Eq. \ref{tent_scaled}, there is a shadowing solution satisfying Eq. \ref{tentmap}: $x_i:= \hat{x}_i/(1+s)$.  The map,
\begin{equation} \label{conjugate_scaled}
    h_s(x):=x/(1+s)
\end{equation}
is known as a \emph{conjugacy} between the two maps $\varphi$ and $\hat{\varphi_s}$ 
because it satisfies
\begin{equation} \label{conjugate_def}
    \varphi(h_s(x)) = h_s(\hat\varphi_s(x))\;,\quad \forall\: x
\end{equation}
or equivalently, $\varphi\circ h_s \equiv h_s\circ\hat\varphi_s$.
Such conjugacy maps can generally help us construct shadowing solutions.
For every solution satisfying
$\hat{\varphi}_s$, $h_s$ maps it to a shadowing solution satisfying $\varphi$.

@@

\subsection{An example of quasi-physical shadowing solution}
\label{sec:sub:quasi-physical-shadow}
The tilted tent map is defined as
\begin{equation} \label{tent_tilted}
    \hat\varphi_s(x) := \begin{cases}
    \frac2{1+s} x \quad & x < 1+s \\
    \frac2{1-s}(2-x) \quad & x \ge 1+s
    \end{cases}
\end{equation}
When $s=0$, this map is identical to the tent map (Eq. \ref{tentmap}).
Let $\tilde{x}_{i+1}=\hat\varphi_s(\tilde{x}_i), i=0,1,\ldots$ be a solution.
As we explained in the previous subsection,
this shadowing solution can be found through a conjugate map $\tilde{h}_s$.
If $\varphi\circ \tilde{h}_s \equiv \tilde{h}_s\circ\tilde\varphi_s$,
then $x_i=\tilde{h}_s(\tilde{x}_i), i=0,1,\ldots$ is a shadowing solution
that satisfies $x_{i+1} = \varphi(x_i)$.

The conjugate map, although more complex than the one
in the last subsection, has the following closed form:
\begin{equation} \label{conjugate_tilted}
    \tilde{h}_s(x) = \sum_{j=0}^{\infty} \frac{\xi_{s,j}(x)}{2^j}\;,
\end{equation}
where
\begin{equation} \label{conjugate_tilted_helper}
    \xi_{s,j}(x) := \begin{cases}
    0 & j=0, x<1+s \\
    1 & j=0, x\ge 1+s \\
    \xi_{s,j-1}(x) & j>0, \tilde\varphi_s^j(x) < 1+s \\
    1 - \xi_{s,j-1}(x) & j>0, \tilde\varphi_s^j(x) \ge 1+s
    \end{cases}
\end{equation}
To see why this map satisfies the definition of the conjugate map --
$\tilde{h}_s(\tilde\varphi_s(x)) = \varphi(\tilde{h}_s(x))$ for all $x$ --
we need to analyze two cases: $x<1+s$ and $x\ge 1+s$.
\begin{figure}[H]
  \centering
    \includegraphics[width=0.48\textwidth]{figure/tilted_tent_map.png}
    \hspace{0.02\textwidth}
    \includegraphics[width=0.48\textwidth]{figure/tilted_conjugate_map.png}
    \\ \vspace{0.02\textwidth}
     \caption{Upper-left: the tilted tent map (\ref{tent_tilted}) for $s=0, 0.1, 0.2, 0.3, 0.4,$ and 0.5.
    Upper-right: the conjugate map $\tilde{h}_s$ between the tent map (\ref{tentmap})
    and the tilted tent map (\ref{tent_tilted}), evaluated using
    Equation (\ref{conjugate_tilted}-\ref{conjugate_tilted_helper}), for the same set of $s$ as the
    upper-left plot.}
     \label{fig:tilted_tent_conjugate}
\end{figure}
When $x<1+s$, $\xi_{s,0}(x)=0$; thus
$\tilde{h}_s(x) = \sum_{j=1}^{\infty} \frac{\xi_{s,j}(x)}{2^j}$.
Inside this infinite series, $\xi_{s,1}(x)=\xi_{s,0}(x)=0$ if $\tilde\varphi_s(x)<1+s$,
or $\xi_{s,1}(x)=1-\xi_{s,0}(x)=1$ if $\tilde\varphi_s(x)\ge 1+s$.
Thus, $\xi_{s,1}(x) = \xi_{s,0}(\varphi_s(x))$ according to the definition of $\xi_{s,0}$.
Using this as the base case, one can inductively verify that
$\xi_{s,j+1}(x) = \xi_{s,j}(\tilde\varphi_s(x))$
for all $j>0$, using just the definition of $\xi_{s,j}$ and $\xi_{s,j+1}$.
Therefore,
$\tilde{h}_s(x) = \frac12 \sum_{j=0}^{\infty} \frac{\xi_{s,j}(\tilde\varphi_s(x))}{2^j}
=\frac12 \tilde{h}_s(\tilde\varphi_s(x))$.
On the other hand, because
$\tilde{h}_s(x) = \sum_{j=1}^{\infty} \frac{\xi_{s,j}(x)}{2^j}\le1$,
$\varphi(\tilde{h}_s(x)) = 2\tilde{h}_s(x)$ according
to the definition of $\varphi$.  Thus,
$\varphi(\tilde{h}_s(x)) = \tilde{h}_s(\tilde\varphi_s(x))$ holds when $x<1+s$.

>>>>

For every solution $\hat{x}_i,i=0,\ldots$ satisfying Eq. \ref{tent_scaled}, there is a shadowing solution satisfying Eq. \ref{tentmap}: $x_i:= \hat{x}_i/(1+s)$.  The map,
\begin{equation} \label{conjugate_scaled}
    \hat{h}_s(x):=x/(1+s)
\end{equation}
is known as a \emph{conjugacy} between the two maps $\varphi$ and $\hat{\varphi_s}$ 
because it satisfies
\begin{equation} \label{conjugate_def}
    \varphi(\hat{h}_s(x)) = \hat{h}_s(\hat\varphi_s(x))\;,\quad \forall\: x
\end{equation}
or equivalently, $\varphi\circ h_s \equiv h_s\circ\hat\varphi_s$.
Such conjugacy maps can generally help us construct shadowing solutions.
For every solution satisfying
$\hat{\varphi}_s$, $h_s$ maps it to a shadowing solution satisfying $\varphi$.

@@

\subsection{An example of quasi-physical shadowing solution}
\label{sec:sub:quasi-physical-shadow}
The tilted tent map is defined as
\begin{equation} \label{tent_tilted}
    \tilde\varphi_s(x) := \begin{cases}
    \frac2{1+s} x \quad & x < 1+s \\
    \frac2{1-s}(2-x) \quad & x \ge 1+s
    \end{cases}
\end{equation}
When $s=0$, this map is identical to the tent map (Eq. \ref{tentmap}).
Let $\tilde{x}_{i+1}=\tilde\varphi_s(\tilde{x}_i), i=0,1,\ldots$ be a solution of 
$\tilde{\varphi}_s$ that is also a perturbed solution of $\varphi$.
As we explained in the previous subsection,
the corresponding 
shadowing solution, which solves $\varphi$, can be found through a conjugacy map $\tilde{h}_s$ that connects the solutions of $\varphi$ and $\tilde{\varphi}_s$.
If $\varphi\circ \tilde{h}_s \equiv \tilde{h}_s\circ\tilde\varphi_s$,
then $x_i=\tilde{h}_s(\tilde{x}_i), i=0,1,\ldots$ is the shadowing solution 
that satisfies $x_{i+1} = \varphi(x_i)$, corresponding to the perturbed solution 
$\tilde{x}_i,i=0,1,\cdots$.

The conjugacy map, although more complex than the one
in the last subsection, has the following closed form:
\begin{equation} \label{conjugate_tilted}
    \tilde{h}_s(x) = \sum_{j=0}^{\infty} \frac{\xi_{s,j}(x)}{2^j}\;,
\end{equation}
where
\begin{equation} \label{conjugate_tilted_helper}
    \xi_{s,j}(x) := \begin{cases}
    0 & j=0, x<1+s \\
    1 & j=0, x\ge 1+s \\
    \xi_{s,j-1}(x) & j>0, \tilde\varphi_s^j(x) < 1+s \\
    1 - \xi_{s,j-1}(x) & j>0, \tilde\varphi_s^j(x) \ge 1+s.
    \end{cases}
\end{equation}
In the above expression, $\tilde{\varphi}^j_s$ refers to the $j$-time 
composition of $\tilde{\varphi}_s.$ That is, if $\tilde{x}_{j+1} = \tilde{\varphi}_s(\tilde{x}_j), j = 0,1,\cdots,$ is a solution, $\tilde{\varphi}_s^i(\tilde{x}_j) = \tilde{x}_{j+i},\quad i,j = 0,1,\cdots$. 
To see why $\tilde{h}_s$ constructed in Eq. \ref{conjugate_tilted} satisfies the definition of a conjugacy map --
$\tilde{h}_s(\tilde\varphi_s(x)) = \varphi(\tilde{h}_s(x))$ for all $x$ --
we need to analyze two cases: $x<1+s$ and $x\ge 1+s$.
\begin{figure}[H]
  \centering
    \includegraphics[width=0.48\textwidth]{figure/tilted_tent_map.png}
    \hspace{0.02\textwidth}
    \includegraphics[width=0.48\textwidth]{figure/tilted_conjugate_map.png}
    \\ \vspace{0.02\textwidth}
     \caption{Upper-left: the tilted tent map (\ref{tent_tilted}) for $s=0, 0.1, 0.2, 0.3, 0.4,$ and 0.5.
    Upper-right: the conjugate map $\tilde{h}_s$ between the tent map (Eq. \ref{tentmap})
    and the tilted tent map (Eq. \ref{tent_tilted}), evaluated using
    Eq. \ref{conjugate_tilted}-\ref{conjugate_tilted_helper}, for the same set of $s$ as the
    upper-left plot.}
     \label{fig:tilted_tent_conjugate}
\end{figure}
When $x<1+s$, $\xi_{s,0}(x)=0$; thus
$\tilde{h}_s(x) = \sum_{j=1}^{\infty} \frac{\xi_{s,j}(x)}{2^j}$.
Inside this infinite series, $\xi_{s,1}(x)=\xi_{s,0}(x)=0$ if $\tilde\varphi_s(x)<1+s$,
or $\xi_{s,1}(x)=1-\xi_{s,0}(x)=1$ if $\tilde\varphi_s(x)\ge 1+s$.
Thus, $\xi_{s,1}(x) = \xi_{s,0}(\varphi_s(x))$ according to the definition of $\xi_{s,0}$.
Using this as the base case, one can inductively verify that
$\xi_{s,j+1}(x) = \xi_{s,j}(\tilde\varphi_s(x))$
for all $j>0$, using just the definition of $\xi_{s,j}$ and $\xi_{s,j+1}$.
Therefore,
$\tilde{h}_s(x) = \frac12 \sum_{j=0}^{\infty} \frac{\xi_{s,j}(\tilde\varphi_s(x))}{2^j}
=\frac12 \tilde{h}_s(\tilde\varphi_s(x))$.
On the other hand, because
$\tilde{h}_s(x) = \sum_{j=1}^{\infty} \frac{\xi_{s,j}(x)}{2^j}\le1$,
$\varphi(\tilde{h}_s(x)) = 2\tilde{h}_s(x)$ according
to the definition of $\varphi$.  Thus,
$\varphi(\tilde{h}_s(x)) = \tilde{h}_s(\tilde\varphi_s(x))$ holds when $x<1+s$.
